02_DESeq_characterization

### 2019-11-22 analysis/03_DESeq2_characterization.Rmd
table formatting

dt1 <- returnGOgenes(GOterms,control.bldg) 
dt2 <- returnGOgenes(GOterms,bldg.lay) 
dt3 <- returnGOgenes(GOterms,lay.inc.d3)  
dt4 <- returnGOgenes(GOterms,inc.d3.inc.d9)  
dt5 <- returnGOgenes(GOterms,inc.d9.inc.d17)  
dt6 <- returnGOgenes(GOterms,inc.d17.hatch)  
dt7 <- returnGOgenes(GOterms,hatch.n5)  
dt8 <- returnGOgenes(GOterms,n5.n9)

kable(dt1)
kable(dt2) 
kable(dt3) 
kable(dt4) 
kable(dt5) 
kable(dt6) 
kable(dt7) 
kable(dt8)
```

>>>>

dt1 <- returnGOgenes(GOterms,control.bldg) 
kable(dt1)

dt2 <- returnGOgenes(GOterms,bldg.lay) 
kable(dt2)

dt3 <- returnGOgenes(GOterms,lay.inc.d3)  
kable(dt3)

dt4 <- returnGOgenes(GOterms,inc.d3.inc.d9)  
kable(dt4)

dt5 <- returnGOgenes(GOterms,inc.d9.inc.d17)  
kable(dt5)

dt6 <- returnGOgenes(GOterms,inc.d17.hatch)  
kable(dt6)

dt7 <- returnGOgenes(GOterms,hatch.n5)  
kable(dt7)

dt8 <- returnGOgenes(GOterms,n5.n9) 
kable(dt8)
